\Large{Learning to Pivot with Adversarial Networks}

### 2016-11-02 tex/paper.tex
last last changes

Proposition~\ref{prop:2} suggests that if at each step of
Algorithm~\ref{alg:adversarial-training} the adversary $r$ is allowed to reach
its optimum given $f$ (e.g., by setting $K$ sufficiently high) and if $f$ is
updated to improve ${\cal L}_f(\theta_f) -  H({Z|f(X;\theta_f)})$ with
sufficiently small steps, then $f$ should eventually
converge to a classifier that is both
optimal and pivotal. Provided this classifier exists, the adversarial term ${\cal L}_r$
can therefore be regarded as a way to select among
the class of all optimal classifiers a function $f$ that is also pivotal.
Despite the former theoretical characterization of the minimax solution
of Eqn.~\ref{eqn:min_thetaf}, let us note that formal guarantees of
convergence towards that solution by
Algorithm~\ref{alg:adversarial-training} in the case where a finite number $K$
of steps is taken for $r$ remains to be proven.

>>>>

Proposition~\ref{prop:2} suggests that if at each step of
Algorithm~\ref{alg:adversarial-training} the adversary $r$ is allowed to reach
its optimum given $f$ (e.g., by setting $K$ sufficiently high) and if $f$ is
updated to improve ${\cal L}_f(\theta_f) -  H({Z|f(X;\theta_f)})$ with
sufficiently small steps, then $f$ should converge to a classifier that is both
optimal and pivotal, provided such a classifier exists. Therefore, the adversarial term ${\cal L}_r$
can be regarded as a way to select among
the class of all optimal classifiers a function $f$ that is also pivotal.
Despite the former theoretical characterization of the minimax solution
of Eqn.~\ref{eqn:min_thetaf}, let us note that formal guarantees of
convergence towards that solution by
Algorithm~\ref{alg:adversarial-training} in the case where a finite number $K$
of steps is taken for $r$ remains to be proven.
